%% Enter letter date here
\newdate{letterdate}{19}{02}{2016}

%% Enter recipient address here
\renewcommand{\recip}{Perimeter Institute}
\renewcommand{\comp}{ Summer Undergraduate Program} %recip suffix
\renewcommand{\recipaddress}{31 Caroline Street North\\
Waterloo, Ontario\hspace{6pt}N2L~2Y5\\
Canada}

%% Enter sender address prefeix and suffix here
\renewcommand{\addressprefix}{}
\renewcommand{\addresssuffix}{\\
(604) 222-1047 ext. 6859
%| cell: (778) 999-6006\\
| \href{mailto:lighthall@triumf.ca}{lighthall@triumf.ca}\\%
}

\ltrwrapper{\workaddress}{%two arguments: address, text
My name is Dr.\ Jon Lighthall and I am a postdoctoral research fellow at TRIUFM in Canada.
I am writing to recommend Lily-belle Sweet as a summer student at \recip.
I have worked with Ms.\ Sweet on a data analysis project at TRIUMF since October, 2015. Her involvement in the project arose form her inquiries with the laboratory requesting some hands-on experience with data analysis. She sought out this extra curricular project while studying abroad and taking a full course load, which exhibits excellent initiative, motivation, and time management.

In our work together, Ms.\ Sweet has demonstrated exceptional independence, creativity, and problem solving. On a typical day working together, I give Ms.\ Sweet a general outline of the analysis goal that I would like her to complete. She consistently shows the ability to synthesize complex information and work independently, finding elegant solutions to complex problems with little guidance. Ms.\ Sweet is able to clearly articulate technical information in both spoken and written communication.

In the time that I have known her, Ms.\ Sweet has shown herself to be one of the most promising physics students that I have worked with.
}
